Reducing iptables configuration complexity using chains

### 2014-05-09 iptables/presentation.tex
mention reason for closing custom chain
add pages about using default target for custom chains
mention netfilter with iptables
Revert "create seperate page for IPv6 only day"
This reverts commit bfb9d3acdd39dc891688a60c0649f0c63aca73cc.

      \item Brief introduction to iptables

@@

    \frametitle{What is iptables?}

@@

@@

  \begin{frame}
    \frametitle{Conclusion}
    \begin{itemize}
      \item use ESTABLISHED state to reduce number of rules
      \item using chains makes your rules easier readable and maintainable
      \item chains can be reused for several rules
      \item chains can be chained together
      \item faster, because it only jumps to a chain when a rule matches
    \end{itemize}
  \end{frame}
  \begin{frame}
   \frametitle{Questions}
    Thanks for your attention!\\
    Questions?
    \vfill
    Contact
    \begin{itemize}
      \item Blog : \href{http://ruleant.blogspot.com/}{http://ruleant.blogspot.com}
      \item Twitter : \href{https://twitter.com/dcadriaenssens}{@dcadriaenssens}
    \end{itemize}
  \end{frame}
  \begin{frame}
    \frametitle{IPv6}
    Configuration is the same for IPv4, use \textit{ip6tables} :
    \begin{example}
      \small{ip6tables -P INPUT DROP\\
      ip6tables -P OUTPUT ACCEPT\\
      ip6tables -A INPUT -i lo -j ACCEPT \# allow local traffic\\
      ip6tables -A INPUT -p icmp -j ACCEPT \# allow ping, etc\\
      ip6tables -A INPUT -m state \dd state ESTABLISHED -j ACCEPT\\
      ip6tables -A INPUT -m state \dd state RELATED -j ACCEPT}
    \end{example}
    Even if IPv4 rules are set, IPv6 has to be configured seperately, otherwise the defaults apply.
  \end{frame}
  \begin{frame}
    \frametitle{IPv6 only day}
    \begin{columns}
      \begin{column}{5cm}
        \includegraphics[scale=.3]{pictures/World_IPv6_launch_badge_512.png}
      \end{column}
      \begin{column}{6cm}
        \textbf{June 6th 2014}\\

        Disable IPv4 for one day!
      \end{column}
    \end{columns}
  \end{frame}
\end{document}

>>>>

      \item Brief introduction to iptables/netfilter

@@

    \frametitle{What is iptables/netfilter?}

@@

    \frametitle{Why you should set a default target}
    Avoid jumping back to the calling chain :
      \item performance issue
      \item unexpected behaviour, some other rules might match

@@

  \begin{frame}
    \frametitle{Conclusion}
    \begin{itemize}
      \item use ESTABLISHED state to reduce number of rules
      \item using chains makes your rules easier readable and maintainable
      \item chains can be reused for several rules
      \item chains can be chained together
      \item faster, because it only jumps to a chain when a rule matches
    \end{itemize}
  \end{frame}
  \begin{frame}
   \frametitle{Questions}
    Thanks for your attention!\\
    Questions?
    \vfill
    Contact
    \begin{itemize}
      \item Blog : \href{http://ruleant.blogspot.com/}{http://ruleant.blogspot.com}
      \item Twitter : \href{https://twitter.com/dcadriaenssens}{@dcadriaenssens}
    \end{itemize}
  \end{frame}
  \begin{frame}
    \frametitle{IPv6}
    Configuration is the same for IPv4, use \textit{ip6tables} :
    \begin{example}
      \small{ip6tables -P INPUT DROP\\
      ip6tables -P OUTPUT ACCEPT\\
      ip6tables -A INPUT -i lo -j ACCEPT \# allow local traffic\\
      ip6tables -A INPUT -p icmp -j ACCEPT \# allow ping, etc\\
      ip6tables -A INPUT -m state \dd state ESTABLISHED -j ACCEPT\\
      ip6tables -A INPUT -m state \dd state RELATED -j ACCEPT}
    \end{example}
    Even if IPv4 rules are set, IPv6 has to be configured seperately, otherwise the defaults apply.\\
    \pause
    \textbf{IPv6 day (June 6th 2014)} $\rightarrow$ disable IPv4 for one day
  \end{frame}
\end{document}
